---
title: "Credibility of Economic Research"
subtitle: "Four Pillars, and Thoughts on Future Paths"
author:
  - Lars Vilhuber
date: "TBD"
---

```{r config,include=FALSE}
library(here)

# The repository name

message(Sys.getenv("GITHUB_REPOSITORY"))

# Process the repository name to generate the URL
# - split the two components
# - combine them into a URL with 'github.io' in the middle

GITHUB_REPOSITORY <- Sys.getenv("GITHUB_REPOSITORY")
GITHUB_REPOSITORY_PARTS <- strsplit(GITHUB_REPOSITORY, "/")[[1]]
REPOSITORY_URL <- paste0("https://github.com/", GITHUB_REPOSITORY)
WEBSITE_URL <- paste0("https://", GITHUB_REPOSITORY_PARTS[1], ".github.io/", GITHUB_REPOSITORY_PARTS[2])
```

<!--
This is the article-length, textual companion to the slide deck in `presentation/`.
It follows the same four-pillar structure. Each section below is scaffolding:
a short lead-in plus a TODO marking what still needs to be written out in full.
Cross-check against `presentation/*.md` for the talking points to expand on,
and replace the [TODO: ...] and [TBD] markers with real prose/citations.
-->

## Introduction

<!-- TODO: motivate the "credibility of economic research" framing; why four pillars, why now -->

Economic research earns its credibility along (at least) four largely independent
dimensions: the quality of its data, the provenance of that data, the quality of
its code, and the quality of its documentation. This article expands, in prose,
on a talk of the same name; it follows the same four pillars and closes with some
thoughts on future paths.

## The Four Pillars

<!-- TODO: expand into a short paragraph per pillar, cross-referencing the slide deck's overview slide (presentation/10-overview.md) -->

- **A — Data quality**: data exists, and is of sufficient quality
- **B — Data provenance**: trustworthy, open / accessible
- **C — Code**: exists, works, is reusable, comprehensible
- **D — Documentation**: papers, README, actionable info

## Pillar A: Data Quality

<!-- TODO: expand on administrative vs. survey vs. business data, "fit for purpose," and
     the challenges introduced by LLM-generated data (see presentation/20-pillar-a-data-quality.md) -->

## Pillar B: Data Provenance

<!-- TODO: expand on gold standards (statistical agencies, DOI/curation), traditional
     concerns (data falsification cases), and the open question of LLM-invented data
     (see presentation/21-pillar-b-provenance.md, 03-sp500.md, 05-fraud.md, 10-what-can-you-do.md) -->

## Pillar C: Code

<!-- TODO: expand on capturing code quality, reproducibility statistics, and how this
     connects to data availability (see presentation/22-pillar-c-code.md) -->

## Pillar D: Documentation

<!-- TODO: expand on documentation statistics and the recurring issues (too brief,
     insider knowledge, undocumented) (see presentation/23-pillar-d-documentation.md) -->

## Thoughts on Future Paths

<!-- TODO: expand per-pillar forward-looking material, including the role of AI/LLMs
     in data provenance, code quality, and documentation
     (see presentation/90-thoughts-future-paths.md) -->

## Conclusion

<!-- TODO: closing synthesis -->

```{r, child=c(here::here('99-links.md'))}
```
